Carbonate chemistry at Ny-Ålesund: AWIPEV-CO~2~ Project

### 2020-04-26 awipev-CO2.Rmd
AWIPEV-CO2 functional again but to be checked

pH_durafet <- d %>%
  dplyr::filter(!is.na(pH_s_durafet))
pH_durafet <- pH_durafet %>%
  dplyr::mutate(ph_s_dur_temp_fb = pHinsi(pH=pH_durafet$pH_s_durafet, ALK=pH_durafet$at_mean_interp*1e-6, Tinsi=pH_durafet$temp_fb, Tlab=pH_durafet$temp_s_lab, Pinsi= pH_durafet$depth/10, S=pH_durafet$sal_fb,Pt=0,Sit=0))

>>>>

pH_durafet <- d %>%
#  dplyr::filter(!is.na(pH_s_durafet))
    dplyr::filter(!is.na(pH_s_durafet) & !is.na(sal_fb) & !is.na(temp_fb))
pH_durafet <- pH_durafet %>%
  dplyr::mutate(ph_s_dur_temp_fb = pHinsi(pH=pH_durafet$pH_s_durafet, ALK=pH_durafet$at_mean_interp*1e-6, Tinsi=pH_durafet$temp_fb, Tlab=pH_durafet$temp_s_lab, Pinsi= pH_durafet$depth/10, S=pH_durafet$sal_fb, Pt=0, Sit=0))
